Air cargo load and route planning in pickup and delivery operations

### 2024-02-02 latex/eswa.tex
New experiments with the shortest tours
Tables  12, 13 and 14 updated
Plots

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.2$\/ and $tmax =  3600s$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}&$method$&$scenario$&{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&\specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} &\multirow{2}{*}{$Gurobi$}  & $f$ & 8.61    & 11.56   & 13.67   & 13.87 & 12.48       &  0.9985 \\ % best 6028
		&                              &               {time (s)}   & 26      & 22      & 28      & 28    & 25          &  1.0    \\ % longer 129
		\cmidrule(lr){2-9}
		&                           \multirow{2}{*}{$Shims$}  & $f$ & 8.61    & 11.56   & 13.46   & 13.93 & 12.51       &  0.9965 \\
		&                             &                {time (s)}   & 1       & 1       & 1       & 1     & 1           &  25.8   \\

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.5$\/ and $tmax =  3600s$}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}} & $method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ Shortest } & \multirow{2}{*}{$Gurobi$} & $f$ & 11.76 & 16.29 & 18.02 & 19.42 & 16.35 & 0.9994 \\ % best 8189
		&&               {time (s)}                                   & 51    & 39    & 40    & 36    & 38    & 1.0 \\ 
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.78 & 16.29 & 17.96 & 19.43 & 16.37 & 0.9993  \\
		&&         {time (s)}                                         & 1     & 1     & 2     & 2     & 2     & 25.5  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$}   & $f$ & 11.76 & 16.37 & 18.01 & 20.95 & 17.60 & 0.9999 \\  % best 8469
		&&               {time (s)}                                   & 64    & 58    & 195   & 472   & 2258  & 1.0  \\
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.78 & 16.29 & 17.99 & 20.93 & 17.50 & 0.9976  \\ 
		&&         {time (s)}                                         & 1     & 2     & 5     & 15    & 100   & 23.8 \\
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 2.0$\/ and $tmax =  3600s$}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}& $method$& $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.89 & 24.96 & 26.15 & 27.52 & 23.85 & 0.9996 \\ % best 12042
		&&                                              {time (s)}  & 183   & 87    & 73    & 79    & 71    & 1.0  \\
		\cmidrule(lr){2-9}	
		&                            \multirow{2}{*}{$Shims$} & $f$ & 17.94 & 24.96 & 26.03 & 27.43 & 23.73 & 0.9972  \\
		&&                                              {time (s)}  & 1     & 2     & 2     & 3     & 4     & 41.1  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.90 & 25.44 & 26.15 & 29.13 &{\bf x}& 0.9994 \\ % best 9867
		&&                                               {time (s)} & 178   & 143   & 378   & 862   &{\bf x}& 1.0  \\
		\cmidrule(lr){2-9}	
		&                         \multirow{2}{*}{$Shims$}    & $f$ & 17.94 & 25.45 & 26.14 & 28.84 & 26.22  & 0.9970  \\
		&&                                               {time (s)} & 1     & 3     & 10    & 31    & 196    & 34.7  \\
		\bottomrule

@@

>>>>

\begin{table}[htp] % update this
	\centering
	\caption{Solutions with $surplus = 1.2$\/ and $tmax =  3600s$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}&$method$&$scenario$&{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&\specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} &\multirow{2}{*}{$Gurobi$}  & $f$ & 8.53    & 11.79   & 13.14   & 13.52 & 12.36       &  0.9998 \\ % best 5935
		&                              &               {time (s)}   & 29      & 28      & 25      & 27    & 27          &  1.0    \\ % longer 136
		\cmidrule(lr){2-9}
		&                           \multirow{2}{*}{$Shims$}  & $f$ & 8.54    & 11.78   & 13.06   & 13.51 & 12.34       &  0.9980 \\
		&                             &                {time (s)}   & 1       & 1       & 1       & 1     & 2           &  22.7   \\

@@

\begin{table}[htp]
	\centering
	\caption{Solutions with $surplus = 1.5$\/ and $tmax =  3600s$}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}} & $method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ Shortest } & \multirow{2}{*}{$Gurobi$} & $f$ & 11.83 & 16.73 & 18.07 & 18.83 & 16.86 & 0.9996 \\ % best 8235
		&&               {time (s)}                                   & 55    & 64    & 39    & 40    & 88    & 1.0    \\ 
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.85 & 16.72 & 18.05 & 18.80 & 16.87 & 0.9993  \\
		&&         {time (s)}                                         & 1     & 1     & 2     & 2     & 2     & 35.8  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$}   & $f$ & 11.83 & 16.93 & 18.40 & 20.95 & 17.60 & 0.9999 \\  % best 8469
		&&               {time (s)}                                   & 63    & 59    & 195   & 472   & 2258  & 1.0  \\
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.85 & 16.91 & 18.36 & 20.93 & 17.50 & 0.9976  \\ 
		&&         {time (s)}                                         & 1     & 2     & 5     & 15    & 100   & 23.8 \\
		\bottomrule

@@

\begin{table}[htp]
	\centering
	\caption{Solutions with $surplus = 2.0$\/ and $tmax =  3600s$}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}& $method$& $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.70 & 24.20 & 26.39 & 27.17 & 24.20 & 0.9995 \\ % best 11972
		&&                                              {time (s)}  & 168   & 98    & 79    & 70    & 72    & 1.0  \\
		\cmidrule(lr){2-9}	
		&                            \multirow{2}{*}{$Shims$} & $f$ & 17.74 & 24.22 & 26.32 & 27.07 & 23.13 & 0.9896  \\
		&&                                              {time (s)}  & 1     & 2     & 2     & 3     & 4     & 40.6  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.90 & 25.44 & 26.51 & 29.13 &{\bf x}& 0.9994 \\ % best 9867
		&&                                               {time (s)} & 178   & 143   & 378   & 862   &{\bf x}& 1.0  \\
		\cmidrule(lr){2-9}	
		&                         \multirow{2}{*}{$Shims$}    & $f$ & 17.94 & 25.45 & 26.44 & 28.84 & 26.22  & 0.9970  \\
		&&                                               {time (s)} & 1     & 3     & 10    & 31    & 196    & 34.7  \\
		\bottomrule

@@

\begin{table}[htp]
	\centering
	\caption{Shims solutions with $surplus = 1.2$\/ and $tmax =  240s$}  \label{tab:15}
	\footnotesize
	\begin{tabular}{cccc}
		\toprule
$scenario$ & {\bf 7} & {\bf 8} & {\bf 9} \\
Num. nodes & 15 & 14 & 13 \\
		\toprule
$f$        & 50.15 & 47.00 & 47.18    \\
{time (s)} & 32     & 31     & 29        \\
Occupancy rate & 0.89     & 0.84     & 0.88        \\
		\bottomrule
	\end{tabular}
	\normalsize
\end{table}

\begin{center}
	%\fbox{
	\begin{tikzpicture}
		\begin{axis}[xmin=6,ymin=200,
			enlarge y limits={upper,value=0.2},
			xlabel style={align=center},
			xlabel={Number of nodes},
			ylabel={Time (s)},
			xtick={  5,   6, 7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
			ytick={250,350,450,550,650,750,850,950,1050,1150,1250},						
			]
			\addplot[
			blue,
			thick,
			mark=*,
			mark options={fill=blue},
			visualization depends on=\thisrow{alignment} \as \alignment,
			nodes near coords, % Place nodes near each coordinate
			point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
			every node near coord/.style={anchor=\alignment} % Align each coordinate at the anchor 40 degrees clockwise from the right edge
			] table [% Provide data as a table
			meta index=2 % the meta data is found in the third column
			] {
				x   y    label                  alignment
				7   273   {\footnotesize 92.6}  -10
				8   360   {\footnotesize 107.5} -10
				9   468   {\footnotesize 107.5} -10
				10  560   {\footnotesize 112.3} -10
				11  660   {\footnotesize 92.8}  -10
				12  756   {\footnotesize 91.2}  -10
				13  884   {\footnotesize 96.8}  -10
				14  1008   {\footnotesize 106.3} -10									
				15  1170   {\footnotesize 99.8}  -10									
			};
		\end{axis}
	\end{tikzpicture}
	%}
	\captionof{figure}{Shims performance}
\end{center}

\begin{center}
	%\fbox{
		\begin{tikzpicture}
			\begin{axis}[xmin=6,ymin=600,
				enlarge y limits={upper,value=0.2},
				xlabel style={align=center},
				xlabel={Number of nodes},
				ylabel={Time (s)},
				xtick={  5,  6,   7,   8,   9,  10,  11,  12,  13,  14,  15,  16},
				ytick={700,860,1020,1180,1340,1500,1660,1820,1980,2140,2300,2460},						
				]
				\addplot[
				blue,
				thick,
				mark=*,
				mark options={fill=blue},
				visualization depends on=\thisrow{alignment} \as \alignment,
				nodes near coords, % Place nodes near each coordinate
				point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
				every node near coord/.style={anchor=\alignment} % Align each coordinate at the anchor 40 degrees clockwise from the right edge
				] table [% Provide data as a table
				meta index=2 % the meta data is found in the third column
				] {
					x   y    label                 alignment
					7   708  {\footnotesize 91.9}  -10
					8   837  {\footnotesize 108.2} -10
					9   987  {\footnotesize 108.7} -10
					10  1160 {\footnotesize 111.2} -10
					11  1354 {\footnotesize 78.0}  -10
					12  1574 {\footnotesize 84.1}  -10
					13  1814 {\footnotesize 93.3}  -10
					14  2083 {\footnotesize 104.8} -10									
					15  2383 {\footnotesize 96.1}  -10									
				};
			\end{axis}
		\end{tikzpicture}
		%}
	\captionof{figure}{Shims performance (total time)}
\end{center}
